---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: Arial, sans-serif;
  line-height: 1.6;
  background-color: #f4f4f4;
}

h1, h2 {
  color: #2c3e50;
}
```

## Observations on Ad Interactions and Relevance on social media
In this report, I will explore data collected from my observations of ads on social media platforms. The goal is to understand the frequency and relevance of ads shown to users and how they interact with these ads. The dataset contains multiple observations recorded over a period of time, where I tracked:
- The social media platform used
- The type of content I was engaging with before seeing the ad
- The number of ads shown during each observation
- The relevance of the ads
- Whether I interacted with the ads and how often

```{r}
# Bar chart for Ad Interaction Frequency by Platform
ggplot(latest_data, aes(x = Platform, fill = AdInteractionFrequency)) +
  geom_bar() +
  labs(title = "Frequency of Ad Interactions by Platform", 
       x = "Social Media Platform", 
       y = "Number of Interactions") 

# Bar chart for Ad Relevance by Platform
ggplot(latest_data, aes(x = Platform, fill = AdRelevance)) +
  geom_bar() +
  labs(title = "Ad Relevance by Platform", 
       x = "Social Media Platform", 
       y = "Number of Ads")

# Calculate average ad relevance
avg_ad_relevance <- mean(latest_data$AdRelevance, na.rm = TRUE)

# Add dynamic comment
paste0("The average ad relevance across all platforms is ", round(avg_ad_relevance, 2))

```
